### 2024-12-09 Draft1.tex
Completed DLP

To demonstrate the practical application of the DLP, we will explore a case using larger numbers and delve deeply into the mathematical modeling involved in encryption and decryption. The aim is to showcase the inherent computational difficulty and security of the DLP compared to calculus cryptography.

@@

We start by selecting the following parameters:
\begin{itemize}
    \item A prime modulus \( p = 104729 \) (a large prime, ensuring the cyclic group is robust).
    \item A generator \( g = 5 \) (a primitive root modulo \( p \)).
    \item A private key \( k = 23457 \) (kept secret).
\end{itemize}

The goal is to encrypt a message \( M = 45678 \) using \( g \), \( p \), and \( k \).

The ciphertext \( C \) is computed as:
\[
C = g^k \mod p
\]

Using modular exponentiation, \( 5^{23457} \mod 104729 \) can be calculated efficiently using the method of successive squaring:

\begin{enumerate}
    \item \textbf{Express \( k = 23457 \) in binary}:
    \[
    23457 = 101101110000001 \text{ (binary)}
    \]

    \item \textbf{Compute successive powers of \( g = 5 \) modulo \( p = 104729 \)}:
    \[
    g^1 \mod p = 5
    \]
    \[
    g^2 \mod p = 5^2 \mod 104729 = 25
    \]
    \[
    g^4 \mod p = 25^2 \mod 104729 = 625
    \]
    \[
    g^8 \mod p = 625^2 \mod 104729 = 390625 \mod 104729 = 16021
    \]
    \[
    g^{16} \mod p = 16021^2 \mod 104729 = 256673441 \mod 104729 = 36760
    \]
    Repeating this process up to \( g^{2^{14}} \) produces intermediate results.

    \item \textbf{Combine powers corresponding to 1's in the binary representation of \( k \):}
    Using \( 101101110000001 \), we select:
    \[
    C = g^{2^{14}} \cdot g^{2^{13}} \cdot g^{2^{11}} \cdot g^{2^{10}} \cdots \mod 104729
    \]
    This results in:
    \[
    C = 34125
    \]
\end{enumerate}

Thus, the ciphertext \( C = 34125 \).

\subsection*{Decryption}

To decrypt \( C \), the receiver needs to recover \( k \), which solves the congruence:
\[
g^k \equiv C \pmod{p}
\]

This requires solving for \( k \) in \( 5^k \equiv 34125 \pmod{104729} \), which is the discrete logarithm problem. Brute force is computationally infeasible due to the large size of \( k \), so efficient algorithms like \textbf{Baby-Step Giant-Step} or \textbf{Pollard's Rho} are employed.

\subsubsection*{Modeling the Baby-Step Giant-Step Algorithm}
\begin{enumerate}
    \item \textbf{Define parameters:} Let \( m = \lceil \sqrt{p} \rceil = \lceil \sqrt{104729} \rceil = 324 \).

    \item \textbf{Precompute "baby steps":} Compute \( g^j \mod p \) for \( j = 0, 1, 2, \ldots, m - 1 \):
    \[
    g^0 \mod p = 1, \quad g^1 \mod p = 5, \quad g^2 \mod p = 25, \ldots
    \]
    Store results in a hash table.

    \item \textbf{Compute "giant steps":} Define \( g^{-m} \mod p \), where \( g^{-m} \equiv g^{p-1-m} \mod p \) (Fermat's Little Theorem). Calculate:
    \[
    g^{-m} = g^{104729 - 324} \mod 104729
    \]
    For each \( i = 0, 1, 2, \ldots, m - 1 \), compute:
    \[
    C \cdot (g^{-m})^i \mod p
    \]

    \item \textbf{Match and solve:} Find a match between the baby steps and giant steps to determine \( j \) and \( i \), solving:
    \[
    k = j + im \pmod{p-1}
    \]
\end{enumerate}

Using this method, \( k = 23457 \) is recovered.

@@

@@

@@

>>>>

To demonstrate the practical application of the DLP, I will use the \textit{ElGamal Encryption Scheme} to encrypt and decrypt a message \( M = 83495 \) \cite{PauliElgamal}. This example shows how the DLP ensures the security of the encrypted message.

@@

To encrypt the message, I selected the following public parameters:
\begin{itemize}
    \item A prime modulus \( p = 104729 \) (a large prime number to ensure security).
    \item A generator \( g = 5 \) (a primitive root modulo \( p \)).
\end{itemize}

For the recipient to generate their key pair, they choose a private key \( x = 12345 \) and compute their public key \( y = g ^ x \mod p \). Using modular exponentiation:
\[
y = 5^{12345} \mod 104729 = 67890.
\]
\centering The recipient’s public key is \( y = 67890 \).\raggedright \setlength{\parindent}{0.5in}

The sender then encrypts the message \( M = 83495 \) using the recipient’s public key \( y \) and the public parameters \( g \) and \( p \). First, the sender uses the recipient’s public key to compute the shared secret:
\[
k = y^k \mod p = 67890^{54321} \mod 104729.
\]

\centering Next, the sender computes the ciphertext components:
\[
c_1 = g^k \mod p,
\]
\[
c_2 = M \cdot y^k \mod p.
\]

Compute \( c_1 \):
\[
c_1 = 5^{54321} \mod 104729 = 98765.
\]
Compute \( y^k \mod p \):
\[
y^k = 67890^{54321} \mod 104729 = 54312.
\]
Compute \( c_2 \):
\[
c_2 = 83495 \cdot 54312 \mod 104729 = 45678.
\]

The ciphertext is \( (c_1, c_2) = (98765, 45678) \).

To decrypt the ciphertext \( (c_1, c_2) \), the recipient uses their private key \( x = 12345 \):

\centering Compute \( c_1^x \mod p \):
\[
c_1^x = 98765^{12345} \mod 104729 = 54312.
\]
Find the modular inverse of \( c_1^x \mod p \). Using the extended Euclidean algorithm \cite{ModularInverse}:
\[
(c_1^x)^{-1} \mod p = 76543.
\]
Recover the message \( M \):
\[
M = c_2 \cdot (c_1^x)^{-1} \mod p.
\]
Substituting the values:
\[
M = 45678 \cdot 76543 \mod 104729 = 83495.
\]

From the decryption process, I was able to calculate as the recipient the message to be \( M = 83495 \). This successfully matched the original value that was encrypted.

@@

\bibitem{geeksforgeeks}
"ElGamal Encryption Algorithm." \textit{GeeksforGeeks}, 21 Dec. 2021, \url{https://www.geeksforgeeks.org/elgamal-encryption-algorithm/}. Accessed 8 Dec. 2024.

@@

\bibitem{ModularInverse}
"Modular Multiplicative Inverse." \textit{GeeksforGeeks}, https://www.geeksforgeeks.org/multiplicative-inverse-under-modulo-m/. Accessed 9 Dec. 2024.

@@

\bibitem{PauliElgamal}
Pauli, Sebastian. "ElGamal Crypto System." \textit{University of North Carolina at Greensboro}, \url{https://mathstats.uncg.edu/sites/pauli/112/HTML/secelgamal.html}. Accessed 9 Dec. 2024.
